Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw

>>>>

\begin{figure}
  \caption{The trend of weekly cooks over time}
  \label{weeklyCooks_Trend}

<<WeeklyCooks, echo=FALSE>>=
figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
print(figureWeeklyCooks)
@

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to the weekly cooks they made. The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}

\begin{figure}
  \caption{The Trend of monthly cooks over time}
  \label{monthlyCooks_Trend}

<<MonthlyCooks, echo=FALSE>>=
figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
print(figureMonthlyCooks)
@

\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012. The y-axis represents the average answers from the organizations regarding to the monthly cooks they made. The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line. Additionally, the linear trends of both groups are included as the straight lines.}
\end{figure}
